---
title: "A corpus-based analysis of adjective amplification in New Zealand English - Part 3"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::html_document2: default
bibliography: bibliography.bib
link-citations: yes
---

This document shows an analysis that was performed with the aim of investigating ongoing changes in the adjective ampplifier system of New Zealand English (NZE) and to determine how innovative variants come to dominate the NZE amplifier system based on the Wellington Spoken Corpus (WSC). The following represents part 3 of this analysis.

In a first step, we prepare the session by cleaning the workspace, loading packages, setting options, and defining paths.

```{r adjampnze_3_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# remove all lists from the current workspace
rm(list=ls(all=T))
# load libraries
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
# set options
options(stringsAsFactors = F)
options(scipen = 999)
options(max.print=10000)
# define image directory
imageDirectory<-"images"
```

Next, we load the data, remove superfluous columns, and inspect the adjectives.

```{r adjampnze_3_02, echo=T, eval = T, message=FALSE, warning=FALSE}
# load data
reallywsc <- read.delim("datatables/ampwsc_regdat.txt", sep = "\t", header = T, skipNul = T)
# create a really dep. variable
reallywsc <- reallywsc %>%
  dplyr::select(-ID, - FileSpeaker, -Speaker, -File)
# simplify adjective
table(reallywsc$Adjective)[order(table(reallywsc$Adjective), decreasing = T)]
```

Next, we simplify the adjectives by collapsing infrequent types and inspect the new data.

```{r adjampnze_3_03, echo=T, eval = T, message=FALSE, warning=FALSE}
freqadj <- names(table(reallywsc$Adjective))[which(table(reallywsc$Adjective) > 20)]
#reallywsc$Adjective <- ifelse(reallywsc$Adjective %in% freqadj, reallywsc$Adjective, "other")
# factorize variables 
fctr <- c("Adjective", "Ethnicity", "Gender", "Education", "L1", "Age", 
          "Function", "Priming", "SemanticCategory", "Emotionality", "really")
reallywsc[fctr] <- lapply(reallywsc[fctr], factor)
# inspect data
str(reallywsc)
```

Next, we inspect Frequency.

```{r adjampnze_3_04, echo=T, eval = T, message=FALSE, warning=FALSE}
# frequency
summary(reallywsc$Frequency)
```

Now, we scale Frequency and inspect it again.

```{r adjampnze_3_05, echo=T, eval = T, message=FALSE, warning=FALSE}
reallywsc$Frequency <- as.vector(scale(reallywsc$Frequency))
summary(reallywsc$Frequency)
```

Next, we plot Frequency.

```{r adjampnze_3_06, echo=T, eval = T, message=FALSE, warning=FALSE}
plot(reallywsc$Frequency, reallywsc$really)
abline(lm(reallywsc$really ~reallywsc$Frequency))
```

Next, we scale Gradability. We begin by inspecting it.

```{r adjampnze_3_07, echo=T, eval = T, message=FALSE, warning=FALSE}
# gradability
reallywsc$Gradability <- as.vector(scale(reallywsc$Gradability-1))
summary(reallywsc$Gradability)
```

Next, we scale Gradability. We begin by inspecting it.

```{r adjampnze_3_08, echo=T, eval = T, message=FALSE, warning=FALSE}
plot(reallywsc$Gradability, reallywsc$really)
abline(lm(reallywsc$really ~ reallywsc$Gradability))
```

Next, we perform the Boruta analysis and begin by using only the variables that we feed to the Boruta analysis, save the data, and start a first Boruta run.

```{r adjampnze_3_09, echo=T, eval = T, message=FALSE, warning=FALSE}
# load library
library(Boruta)
# create dada for boruta
borutadata <- reallywsc %>%
  na.omit()
# save and load data
write.table(borutadata, "datatables/borutadata.txt", sep = "\t", 
            col.names = T, row.names = F, quote = F)
# run 1
boruta.reallywsc <- Boruta(really ~.,data=borutadata)
print(boruta.reallywsc)
```

Next, we extract the confirmed Boruta formula to see which variables are deemed important.

```{r adjampnze_3_10, echo=T, eval = T, message=FALSE, warning=FALSE}
getConfirmedFormula(boruta.reallywsc)
```

Next, we plot the results of the first Boruta run.

```{r adjampnze_3_11, echo=T, eval = T, message=FALSE, warning=FALSE}
png("images/BorutaVeryWsc.png",  width = 1800, height = 300)
plot(boruta.reallywsc, cex = .75)
dev.off()
plot(boruta.reallywsc)
```

Next, we plot the history of the first Boruta run.

```{r adjampnze_3_12, echo=T, eval = T, message=FALSE, warning=FALSE}
png("images/BorutaVeryWsc_History1.png",  width = 680, height = 480)
plotImpHistory(boruta.reallywsc)
dev.off()
plotImpHistory(boruta.reallywsc)
```

Next, we remove those variables that are deemed unimportant by the first Boruta run and proceed with a second run.

```{r adjampnze_3_13, echo=T, eval = T, message=FALSE, warning=FALSE}
# remove superfluous variables
borutadata$Gender <- NULL
borutadata$Function <- NULL
borutadata$Education <- NULL
# run2
boruta.reallywsc <- Boruta(really~.,data=borutadata)
print(boruta.reallywsc)
```

Next, we remove those variables that are deemed unimportant by the first Boruta run and proceed with a second run.

```{r adjampnze_3_14, echo=T, eval = T, message=FALSE, warning=FALSE}

getConfirmedFormula(boruta.reallywsc)

png("images/BorutaVeryWsc2.png",  width = 1200, height = 300)
plot(boruta.reallywsc, cex = .75)
dev.off()
plot(boruta.reallywsc)

png("images/BorutaNSP_History2.png",  width = 680, height = 480)
plotImpHistory(boruta.reallywsc)
dev.off()
plotImpHistory(boruta.reallywsc)

png("images/BorutaVeryWsc_final.png",  width = 1500, height = 750)
par(mar = c(22, 8, 4, 2) + 0.1)
plot(boruta.reallywsc, cex.axis=3, las=2, xlab="", ylab = "", cex = 3, 
     col = c(rep("grey50", 9), rep("grey90",3)))
abline(v = 3.5, lty = "dashed")
mtext("Predictors", 1, line = 21, at = 9, cex = 3)
mtext("Control", 1, line = 21, at = 2, cex = 3)
mtext("Importance", 2, line = 5, at = 25, cex = 3, las = 0)
dev.off()
par(mar = c(5, 4, 4, 2) + 0.1)

###########################################################################
#           MIXED EFFECTS BIONOMIAL LOGISTIC REGRESSION
# load library
library(rms)
# set options
options(contrasts  =c("contr.treatment", "contr.poly"))
reallywsc.dist <- datadist(reallywsc)
options(datadist = "reallywsc.dist")
# generate initial minimal regression model 
m0.glm = glm(really ~ 1, family = binomial, data = reallywsc) # baseline model glm
m0.lrm = lrm(really ~ 1, data = reallywsc, x = T, y = T) # baseline model lrm
# inspect results
summary(m0.glm)

m0.lrm

###########################################################################
# load libraries
library(lme4)
library(car)
# create model with a random intercept for token
m0.lmer <- lmer(really ~ (1|Adjective), data = reallywsc, family = binomial)
# Baayen (2008:278-284) uses the call above but the this call is now longer
# up-to-date becwsce the "family" parameter is deprecated
# we switch to glmer (suggested by R) instead but we will also
# create a lmer object of the final minimal adequate model as some functions
# will not (yet) work on glmer
m0.glmer = glmer(really ~ (1|Adjective), data = reallywsc, family = binomial)

# results of the lmer object
print(m0.lmer, corr = F)

# check if including the random effect is permitted by comparing the aic from the glm to aic from the glmer model
aic.glmer <- AIC(logLik(m0.glmer))
aic.glm <- AIC(logLik(m0.glm))
aic.glmer; aic.glm

# the aic of the glmer object is smaller which shows that including the random
# intercepts is justified

# test random effects
null.id = -2 * logLik(m0.glm) + 2 * logLik(m0.glmer)
pchisq(as.numeric(null.id), df=1, lower.tail=F) # sig m0.glmer better than m0.glm

# inspect results
summary(m0.glm)

summary(m0.glmer)

###########################################################################
# model fitting
# fit the model to find the "best" model, i.e. the minimal adequate model
# we will use a step-wise step up procedure
# we need to add "control = glmerControl(optimizer = "bobyqa")" 
# becwsce otherwise R fails to converge
#	manual modelfitting
m0.glmer <- glmer(really ~ 1 + (1|Adjective), family = binomial, data = reallywsc, 
                  control=glmerControl(optimizer="bobyqa"))
# add Age
ifelse(min(ftable(reallywsc$Age, reallywsc$really)) == 0, "not possible", "possible")
m1.glm <- update(m0.glm, .~.+Age)
m1.glmer <- update(m0.glmer, .~.+Age)
anova(m0.glmer, m1.glmer, test = "Chi")                            # SIG! (p = 0.00000000000000022 ***)
Anova(m1.glmer, type = "III", test = "Chi")                        # SIG! (p = 0.00000000000000022 ***)

# add Adjective
ifelse(min(ftable(reallywsc$Adjective, reallywsc$really)) == 0, "not possible", "possible")
# not possible

# add Frequency
m2.glm <- update(m1.glm, .~.+Frequency)
max(vif(m2.glm)[,1])                                               # VIFs ok
m2.glmer <- update(m1.glmer, .~.+Frequency)
anova(m2.glmer, m1.glmer, test = "Chi")                            # not sig (p=0.618)

# add Emotionality
ifelse(min(ftable(reallywsc$Emotionality, reallywsc$really)) == 0, "not possible", "possible")
m3.glm <- update(m1.glm, .~.+Emotionality)
max(vif(m3.glm)[,1])                                               # VIFs ok
m3.glmer <- update(m1.glmer, .~.+Emotionality)
anova(m3.glmer, m1.glmer, test = "Chi")                            # SIG! (p = 0.00004315 ***)
Anova(m3.glmer, type = "III", test = "Chi")                        # SIG! (p = 0.000146 ***)

# add Ethnicity
ifelse(min(ftable(reallywsc$Ethnicity, reallywsc$really)) == 0, "not possible", "possible")
m4.glm <- update(m3.glm, .~.+Ethnicity)
max(vif(m4.glm)[,1])                                               # VIFs ok
m4.glmer <- update(m3.glmer, .~.+Ethnicity)
anova(m4.glmer, m3.glmer, test = "Chi")                            # not sig (p=0.9503)

# add SemanticCategory
ifelse(min(ftable(reallywsc$SemanticCategory, reallywsc$really)) == 0, "not possible", "possible")
m5.glm <- update(m3.glm, .~.+SemanticCategory)
max(vif(m5.glm)[,1])                                               # VIFs ok
m5.glmer <- update(m3.glmer, .~.+Gradability)
anova(m5.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06859 .)
Anova(m5.glmer, type = "III", test = "Chi")                        # mar sig (p = 0.0683430 .)

# add Gradability
m6.glm <- update(m3.glm, .~.+Gradability)
max(vif(m6.glm)[,1])                                               # VIFs ok
m6.glmer <- update(m3.glmer, .~.+Gradability)
anova(m6.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06859 .)
Anova(m6.glmer, type = "III", test = "Chi")                        # mar sig (p = 0.0683430 .)

# add Priming
ifelse(min(ftable(reallywsc$Priming, reallywsc$really)) == 0, "not possible", "possible")
m7.glm <- update(m3.glm, .~.+Priming)
max(vif(m7.glm)[,1])                                               # VIFs ok
m7.glmer <- update(m3.glmer, .~.+Priming)
anova(m7.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.8786)

# add L1
ifelse(min(ftable(reallywsc$L1, reallywsc$really)) == 0, "not possible", "possible")
m8.glm <- update(m3.glm, .~.+L1)
max(vif(m8.glm)[,1])                                               # VIFs ok
m8.glmer <- update(m3.glmer, .~.+L1)
anova(m8.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.09292 .)
Anova(m8.glmer, type = "III", test = "Chi")                        # mar sig (p = 0.0869448 .)

###########################################################################
# find all 2-way interactions
library(utils)
colnames(reallywsc)

vars <- c("Age", "Frequency", "Emotionality", "Ethnicity", 
          "SemanticCategory", "Gradability", "Priming", "L1")
intac <- t(combn(vars, 2))
intac

# add Age * Frequency
m9.glm <- update(m3.glm, .~.+Age * Frequency)
max(vif(m9.glm)[,1])                                               # high VIFs
m9.glmer <- update(m3.glmer, .~.+Age * Frequency)
anova(m9.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.1792)

# add Age * Emotionality
m10.glm <- update(m3.glm, .~.+Age * Emotionality)
max(vif(m10.glm)[,1])                                              # VIFs unacceptable

# add Age * Ethnicity
m11.glm <- update(m3.glm, .~.+Age * Ethnicity)
max(vif(m11.glm)[,1])                                               
# Error in vif.default(m11.glm) : there are aliased coefficients in the model

# add Age * SemanticCategory
m12.glm <- update(m3.glm, .~.+Age * SemanticCategory)
max(vif(m12.glm)[,1])                                               
# Error in vif.default(m12.glm) : there are aliased coefficients in the model

# add Age * Gradability
m13.glm <- update(m3.glm, .~.+Age * Gradability)
max(vif(m13.glm)[,1])                                               # VIFs ok
m13.glmer <- update(m3.glmer, .~.+Age * Gradability)
anova(m13.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.3312)

# add Age * Priming
m14.glm <- update(m3.glm, .~.+Age * Priming)
max(vif(m14.glm)[,1])                                               # high VIFs
m14.glmer <- update(m3.glmer, .~.+Age * Priming)
anova(m14.glmer, m3.glmer, test = "Chi")                            # SIG! (p = 0.01175 *)
Anova(m14.glmer, type = "III", test = "Chi")                        # SIG! (p = 0.01175 *)
bic <- anova(m14.glmer, m3.glmer, test = "Chi")
ifelse(bic$BIC[2]-bic$BIC[1] < 0, "ok", "BIC inflation!")           # BIC inflation!
# return to model m3.glmer

# add Age * L1
m15.glm <- update(m3.glm, .~.+Age * L1)
max(vif(m15.glm)[,1])                                               # high VIFs
m15.glmer <- update(m3.glmer, .~.+Age * L1)
anova(m15.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2736)

# add Frequency * Emotionality
m16.glm <- update(m3.glm, .~.+Frequency * Emotionality)
max(vif(m16.glm)[,1])                                               # VIFs unacceptable

# add Frequency * Ethnicity
m17.glm <- update(m3.glm, .~.+Frequency * Ethnicity)
max(vif(m17.glm)[,1])                                               # VIFs ok
m17.glmer <- update(m3.glmer, .~.+Frequency * Ethnicity)
anova(m17.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.7228)

# add Frequency * SemanticCategory
m18.glm <- update(m3.glm, .~.+Frequency * SemanticCategory)
max(vif(m18.glm)[,1])                                               # VIFs unacceptable

# add Frequency * Gradability
m19.glm <- update(m3.glm, .~.+Frequency * Gradability)
max(vif(m19.glm)[,1])                                               # VIFs ok
m19.glmer <- update(m3.glmer, .~.+Frequency * Gradability)
anova(m19.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.1545)

# add Frequency * Priming
m20.glm <- update(m3.glm, .~.+Frequency * Priming)
max(vif(m20.glm)[,1])                                               # VIFs ok
m20.glmer <- update(m3.glmer, .~.+Frequency * Priming)
anova(m20.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.1897)

# add Frequency * L1 
m21.glm <- update(m3.glm, .~.+Frequency * L1)
max(vif(m21.glm)[,1])                                               # VIFs ok
m21.glmer <- update(m3.glmer, .~.+Frequency * L1)
anova(m21.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.3614)

# add Emotionality * Ethnicity  
m22.glm <- update(m3.glm, .~.+Emotionality * Ethnicity)
max(vif(m22.glm)[,1])                                               # VIFs unacceptable

# add Emotionality * SemanticCategory 
m23.glm <- update(m3.glm, .~.+Emotionality * SemanticCategory)
max(vif(m23.glm)[,1])                                               
# Error in vif.default(m23.glm) : there are aliased coefficients in the model

# add Emotionality * Gradability 
m24.glm <- update(m3.glm, .~.+Emotionality * Gradability)
max(vif(m24.glm)[,1])                                               # VIFs ok
m24.glmer <- update(m3.glmer, .~.+Emotionality * Gradability)
anova(m24.glmer, m3.glmer, test = "Chi")                            # SIG! (p = 0.004597 **)
Anova(m24.glmer, type = "III", test = "Chi")                        # SIG! (p = 0.0089823 **)
bic <- anova(m24.glmer, m3.glmer, test = "Chi")
ifelse(bic$BIC[2]-bic$BIC[1] < 0, "ok", "BIC inflation!")           # BIC inflation!
# return to model m3.glmer

# add Emotionality * Priming 
m25.glm <- update(m3.glm, .~.+Emotionality * Priming)
max(vif(m25.glm)[,1])                                               # high VIFs
m25.glmer <- update(m3.glmer, .~.+Emotionality * Priming)
anova(m25.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.9929)

# add Emotionality * L1 
m26.glm <- update(m3.glm, .~.+Emotionality * L1)
max(vif(m26.glm)[,1])                                               # high VIFs 
m26.glmer <- update(m3.glmer, .~.+Emotionality * L1)
anova(m26.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06568 .)
Anova(m26.glmer, type = "III", test = "Chi")                        # not sig (p = 0.1294207)

# add Ethnicity * SemanticCategory 
m27.glm <- update(m3.glm, .~.+Ethnicity * SemanticCategory)
max(vif(m27.glm)[,1])                                               # high VIFs 
# Error in vif.default(m27.glm) : there are aliased coefficients in the model

# add Ethnicity * Gradability 
m28.glm <- update(m3.glm, .~.+Ethnicity * Gradability)
max(vif(m28.glm)[,1])                                               # VIFs ok
m28.glmer <- update(m3.glmer, .~.+Ethnicity * Gradability)
anova(m28.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2035)

# add Ethnicity * Priming  
m29.glm <- update(m3.glm, .~.+Ethnicity * Priming)
max(vif(m29.glm)[,1])                                               # VIFs ok
m29.glmer <- update(m3.glmer, .~.+Ethnicity * Priming)
anova(m29.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.9995)

# add Ethnicity * L1   
m30.glm <- update(m3.glm, .~.+Ethnicity * L1)
max(vif(m30.glm)[,1])                                               # VIFs ok
m30.glmer <- update(m3.glmer, .~.+Ethnicity * L1)
anova(m30.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2482)

# add SemanticCategory * Gradability   
m31.glm <- update(m3.glm, .~.+SemanticCategory * Gradability)
max(vif(m31.glm)[,1])                                               # VIFs unacceptable

# add SemanticCategory * Priming   
m32.glm <- update(m3.glm, .~.+SemanticCategory * Priming)
max(vif(m32.glm)[,1])                                               # VIFs unacceptable

# add SemanticCategory * L1   
m33.glm <- update(m3.glm, .~.+SemanticCategory * L1)
max(vif(m33.glm)[,1])                                               # VIFs unacceptable
# Error in vif.default(m33.glm) : there are aliased coefficients in the model

# add Gradability * Priming  
m34.glm <- update(m3.glm, .~.+Gradability * Priming)
max(vif(m34.glm)[,1])                                               # VIFs ok
m34.glmer <- update(m3.glmer, .~.+Gradability * Priming)
anova(m34.glmer, m3.glmer, test = "Chi")                            # SIG! (p = 0.04327 *)
Anova(m34.glmer, type = "III", test = "Chi")                        # SIG! (p = 0.032951 *)
bic <- anova(m34.glmer, m3.glmer, test = "Chi")
ifelse(bic$BIC[2]-bic$BIC[1] < 0, "ok", "BIC inflation!")           # BIC inflation!
# return to model m3.glmer

# add Gradability * L1  
m35.glm <- update(m3.glm, .~.+Gradability * L1)
max(vif(m35.glm)[,1])                                               # VIFs ok
m35.glmer <- update(m3.glmer, .~.+Gradability * L1)
anova(m35.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06003 .)
Anova(m35.glmer, type = "III", test = "Chi")                        # not sig (p = 0.278465)

# add Priming * L1  
m36.glm <- update(m3.glm, .~.+Priming * L1)
max(vif(m36.glm)[,1])                                               # VIFs ok
m36.glmer <- update(m3.glmer, .~.+Priming * L1)
anova(m36.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2725)

#########################################
# calculate power
# load package
library(simr)
# restructure data
preallywsc <- reallywsc %>%
  dplyr::select(Age, Emotionality, Adjective, really) %>%
  dplyr::mutate(other = ifelse(really == "really", 0, 1)) %>%
  dplyr::mutate(really = ifelse(really == "really", 1, 0)) %>%
  dplyr::group_by(Age, Emotionality, Adjective) %>%
  dplyr::summarise(really = sum(really), other = sum(other))
# redo model
gm1 <- glmer(cbind(really, other) ~ Age + Emotionality + (1 | Adjective), data=preallywsc,
             family=binomial)
# perform likelihood ratio test
doTest(gm1, fixed("Age", "lr"))

# set seed for replicability
set.seed(2019121201)
# calculate power for Age
powerSim(m3.glmer, fixed("Age", "lr"), nsim=100)

# set seed for replicability
set.seed(2019121202)
# calculate power for Emotionality
powerSim(gm1, fixed("Emotionality", "lr"), nsim=100)

# check power curve
#pc <- powerCurve(gm1)
# inspect plot
#plot(pc)

#########################################
# load function for regression table summary
source("D:\\R/meblr.summary.R")
# set up summary table
meblrm_ampwsc <- meblrm.summary(m0.glm, m3.glm, m0.glmer, m3.glmer, reallywsc$really) #
meblrm_ampwsc

# save results to disc
write.table(meblrm_ampwsc, "datatables/meblrm_ampwsc.txt", sep="\t")

# load function
library(car)
meblrm_ampwsc_Anova <- Anova(m3.glmer, type = "III", test = "Chi")
meblrm_ampwsc_Anova

# save results to disc
write.table(meblrm_ampwsc_Anova, "datatables/meblrm_ampwsc_Anova.txt", sep="\t")

effectage <- anova(m1.glmer, m0.glmer, test = "Chi")

effectemotionality <- anova(m3.glmer, m1.glmer, test = "Chi")

# use customized model comparison function
# create comparireallyns
m1.m0 <- anova(m1.glmer, m0.glmer, test = "Chi")                            # SIG! (p = 0.00000000000000022 ***)
m2.m1 <- anova(m2.glmer, m1.glmer, test = "Chi")                            # not sig (p=0.618)
m3.m1 <- anova(m3.glmer, m1.glmer, test = "Chi")                            # SIG! (p = 0.00004315 ***)
m4.m3 <- anova(m4.glmer, m3.glmer, test = "Chi")                            # not sig (p=0.9503)
m5.m3 <- anova(m5.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06859 .)
m6.m3 <- anova(m6.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06859 .)
m7.m3 <- anova(m7.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.8786)
m8.m3 <- anova(m8.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.09292 .)
m9.m3 <- anova(m9.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.1792)
m13.m3 <- anova(m13.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.3312)
m14.m3 <- anova(m14.glmer, m3.glmer, test = "Chi")                            # SIG! (p = 0.01175 *)
m15.m3 <- anova(m15.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2736)
m17.m3 <- anova(m17.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.7228)
m19.m3 <- anova(m19.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.1545)
m20.m3 <- anova(m20.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.1897)
m21.m3 <- anova(m21.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.3614)
m24.m3 <- anova(m24.glmer, m3.glmer, test = "Chi")                            # SIG! (p = 0.004597 **)
m25.m3 <- anova(m25.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.9929)
m26.m3 <- anova(m26.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06568 .)
m28.m3 <- anova(m28.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2035)
m29.m3 <- anova(m29.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.9995)
m30.m3 <- anova(m30.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2482)
m34.m3 <- anova(m34.glmer, m3.glmer, test = "Chi")                            # SIG! (p = 0.04327 *)
m35.m3 <- anova(m35.glmer, m3.glmer, test = "Chi")                            # mar sig (p = 0.06003 .)
m36.m3 <- anova(m36.glmer, m3.glmer, test = "Chi")                            # not sig (p = 0.2725)

# create a list of the model comparireallyns
mdlcmp <- list(m1.m0, m2.m1, m3.m1, m4.m3, m5.m3, m6.m3, m7.m3, m8.m3, 
               m9.m3, m13.m3, m14.m3, m15.m3, m17.m3, m19.m3, m20.m3, 
               m21.m3, m24.m3, m25.m3, m26.m3, m28.m3, m29.m3, m30.m3, 
               m34.m3, m35.m3, m36.m3)
# load function
source("D:\\R/ModelFittingSummarySWSU.R") # for Mixed Effects Model fitting (step-wise step-up): Binary Logistic Mixed Effects Models
# apply function
mdl.cmp.glmersc.swsu.dm <- mdl.fttng.swsu(mdlcmp)
# inspect output
mdl.cmp.glmersc.swsu.dm

write.table(mdl.cmp.glmersc.swsu.dm, "datatables/mdl_cmp_glmersc_swsu_reallywsc.txt", sep="\t")
###########################################################
# Post-hoc analysis
library (multcomp)
summary(glht(m3.glmer, mcp(Age="Tukey")))

summary(glht(m3.glmer, mcp(Emotionality="Tukey")))

################################################################
#                 IMPORTANT OBJECTS
################################################################
# inspect really important objects
head(reallywsc)

# glmer
effectage

effectemotionality

meblrm_ampwsc

meblrm_ampwsc_Anova

###############################################################
# predict probs of nativelike for effects
reallywsc$PredictedFrequency <- predict(m3.glmer, reallywsc, type="response")
summary(reallywsc$PredictedFrequency)

# create response variable
reallywsc$PredictedResponse <- ifelse(reallywsc$PredictedFrequency > .5, "really", "other")
summary(reallywsc$PredictedResponse)

# load library
library(caret)
# create confusion matrix
confusionMatrix(as.factor(reallywsc$PredictedResponse), as.factor(reallywsc$really))

# prepare plot data (pd) 
pd <- reallywsc

# effect emotionality
p5 <- ggplot(pd, aes(x = Emotionality, y = PredictedFrequency)) +
  stat_summary(fun.y = mean, geom = "point") +          
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) + 
  coord_cartesian(ylim = c(0, 1)) +
  theme_set(theme_bw(base_size = 20)) +
  #  theme(legend.position="none") +
  labs(x = "Emotionality", y = "Predicted probability\nof really") +
  ggsave(file = paste(imageDirectory,"PredictedEmotionality.png",sep="/"), 
       height = 5,  width = 7,  dpi = 320)
p5

# convert Age column
Agelbs <- names(table(pd$Age))
pd$Age <- ifelse(pd$Age == "16-19", 6,
                 ifelse(pd$Age == "20-29", 5,
                        ifelse(pd$Age == "30-39", 4, 
                               ifelse(pd$Age == "40-49", 3, 
                                      ifelse(pd$Age == "50-59", 2, 
                                             ifelse(pd$Age == "60+", 1, pd$Age))))))
pd$Age<- as.numeric(pd$Age)
# effect age
p6 <- ggplot(pd, aes(x = Age, y = PredictedFrequency)) +
  geom_smooth(aes(y = PredictedFrequency, x = Age), 
              colour="black", size=1, se = T, method = "loess") +
  coord_cartesian(ylim = c(0, 1)) +
  theme_set(theme_light(base_size = 15)) +
  #  theme(legend.position="none") +
  labs(x = "Frequency of adj. type", y = "Predicted probability\nof really") +
  scale_x_continuous(name = "Age",
                     breaks = c(1, 2, 3, 4, 5, 6),
                     labels=rev(Agelbs))
ggsave(file = paste(imageDirectory,"PredictedAge.png",sep="/"), 
       height = 5,  width = 5,  dpi = 320)
p6

library(effects)
png("images/effectsfinalmodel.png",  width = 960, height = 480) 
plot(allEffects(m3.glmer), type="response", ylim=c(0,1), grid=TRUE, 
     lines = list(col="black",
                  lty = 1,
                  confint=list(style="bars",
                               col = "grey80")), 
     ylab = "Prob (really)")
dev.off()

randomtb <- ranef(m3.glmer)
rndmadj <- as.vector(unlist(randomtb$`Adjective`))
adj <- as.vector(unlist(rownames(randomtb$`Adjective`)))
rndmadjtb <- data.frame(adj, rndmadj)
colnames(rndmadjtb) <- c("Adjective", "Intercept")
rndmadjtb <- rndmadjtb[order(rndmadjtb$Intercept, decreasing = T),]
rndmadjtb

p7 <- ggplot(rndmadjtb, aes(Adjective, Intercept)) +
  geom_point(aes(reorder(Adjective, -Intercept, fun = Intercept), y=Intercept)) +
  coord_cartesian(ylim = c(-1.5, 1.5)) +
  theme_set(theme_bw(base_size = 15)) +
  theme(legend.position="none", axis.text.x = element_text(size=15, angle=90)) +
  labs(x = "Adjective type", y = "Adjustment to Intercept")
ggsave(file = paste(imageDirectory,"RanAdjective.png",sep="/"), 
       height = 5,  width = 10,  dpi = 320)
# activate (remove #) to show
p7

###############################################################
write.table(reallywsc, "datatables/reallywsc.txt", row.names= F, sep = "\t")
```

We have reached the end of the analysis.
